{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2022-01-07 Presentation/slides.tex
increment

		\begin{itemize}
			\item Near-infrared (NIR) spectroscopy enables fast diagnostics by using the NIR region of the electromagnetic spectrum
			\item Suited for field-monitoring / on-line analysis and diagnostics of e.g: prediction of octane ratings!
			\item Spectroscopy results in high-dimensional dataset.	
			\item This set of measurements along a continuum can be viewed as set of smooth spectral curves
			\item Regression to determine relationship between octane rating and spectral curves
			\end{itemize}
	\end{frame}

@@

	\begin{frame}{Square Integrable Function}
		If a function $f$ satisfies:
		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
		the function $f$ is called square integrable function
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1] $
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
			\item We focus on $\mathbb{L}^{2} [0,1]$ since the dimension of the domain of our function is 1
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Estimation via Basis Representation}
		Assume the following \textbf{data generating process}
		$$Y(\omega) = \alpha + \int_{0}^{1} \beta(s) F(\omega)(s) \mathrm{d}s + \epsilon(\omega)$$
		\begin{itemize}
			\item $Y(\omega)$ and $\epsilon(\omega)$ realize in $\mathbb{R}$ and $F(\omega)$ realizes in $\mathbb{L}^2[0,1]$
		\end{itemize}
		\vspace{0.2cm}

@@

	\begin{frame}{Simulation Setup \& Application}
		\begin{itemize}
			\item Use the \textbf{gasoline dataset} (NIR-spectroscopy, 60 $\times$ 401) to predict octane ratings.
			\item Generate \textbf{similar curves} from gasoline dataset:
		\end{itemize}

>>>>

		\begin{itemize}
			\item Near-infrared (NIR) spectroscopy enables fast diagnostics by using the NIR region of the electromagnetic spectrum (2,500–750 nm)
			\item Suited for field-monitoring / on-line analysis and diagnostics of e.g: prediction of octane ratings!
			\item Spectroscopy results in high-dimensional dataset.	
			\item This set of measurements along a continuum can be viewed as set of smooth spectral curves
			\item Regression to determine relationship between octane rating and spectral curves
			\end{itemize}
	\end{frame}

@@

	\begin{frame}{Square Integrable Function}
		If a function $f$ satisfies:
		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
		the function $f$ is called square integrable function
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1] $
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Estimation via Basis Representation}
		Assume the following \textbf{Data Generating Process}
		$$Y(\omega) = \alpha + \int_{0}^{1} \beta(s) F(\omega)(s) \mathrm{d}s + \epsilon(\omega)$$
		\begin{itemize}
			\item $Y(\omega)$ and $\epsilon(\omega)$ realize in $\mathbb{R}$ and $F(\omega)$ realizes in $\mathbb{L}^2[0,1]$
		\end{itemize}
		\vspace{0.2cm}

@@

	\begin{frame}{Simulation Setup \& Application}
		\begin{itemize}
			\item Use the \textbf{Gasoline Dataset} (NIR-spectroscopy, 60 $\times$ 401) to predict octane ratings.
			\item Generate \textbf{similar curves} from gasoline dataset:
		\end{itemize}

### 2022-01-07 main.tex
increment

	\subsection{Different Bases of $\mathbb{L}^2$}
	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion. Two examples of orthonormal bases of $\mathbb{L}^2[0,1]$ that are often used in practice are explained in the following.

@@

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
	Given a realization of a random function realizing in $\mathbb{L}^2$, it is possible to represent this realization in terms of its generating stochastic process. To motivate it, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2$. Therefore, let $F: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
	Then the mean and covariance functions of $F$ are defined as follows.

@@

	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathcal{I}\}$ of the following equation.

@@

	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}_i, \hat{\nu}_i) \: \vert \: i \in \mathcal{I}\}$ for $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathcal{I}\}$ as the solutions of the following equation. {\color{red} I think the number of principal components has to be smaller then the number of observations. So I can give more information about $\mathcal{I}$.}

@@

	\begin{equation}
		y = \alpha + \Psi(f) + \epsilon
	\end{equation}

@@

	\begin{equation}
		y = \alpha + \int_{0}^{1} \beta(s)f(s) \mathrm{d}s + \epsilon
	\end{equation}

	Where $f(s)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(s)$ is an unknown coefficient function. 
	Similar to the finite dimensional setting, an interesting question is how to estimate the unknown function $\beta(s)$ given a data set containing realizations of a random function and associated scalar response variables. However, a simple extension of the OLS estimator to allow for infinite dimensional objects is not possible. Therefore, other options have to be considered.

	\subsection{Estimation via Basis-Representation}
	The most common way to make this problem tractable is via a basis representation of the originally observed function.

>>>>

	\subsection{Different Bases of $\mathbb{L}^2$}
	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion. Two examples of bases that are often used in practice to express / approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.

	Both of these can be used to express or in the case of the b-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions. Let therefore $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $F(\omega') = f(t)$ of $F(\omega)$.

	\begin{equation}
		F(\omega') = f(t) = \sum_{j \in \mathcal{I}} \psi_j(\omega') b_j(t)
	\end{equation}

@@

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
	Given a realization of a random function realizing in $\mathbb{L}^2$, it is possible to represent this realization in terms of its generating stochastic process. To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix.

	\begin{equation}
		\text{{\color{red} Introduce spectral representation of random vector here.}}
	\end{equation}

	To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2$. Therefore, let $F: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
	Then the mean and covariance functions of $F$ are defined as follows.

@@

	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathbb{N}\}$ of the following equation.

@@

	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}_i, \hat{\nu}_i) \: \vert \: i \in \mathbb{N}\}$ for $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathbb{N}\}$ as the solutions of the following equation. {\color{red} I think the number of principal components has to be smaller then the number of observations. So I can give more information about $\mathbb{N}$.}

@@

	\begin{equation}
		Y(\omega) = \alpha + \Psi\left(F(\omega)\right) + \epsilon(\omega)
	\end{equation}

@@

	\begin{equation}\label{DGP}
		Y(\omega) = \alpha + \int_{0}^{1} \beta(s)F(\omega)(s) \mathrm{d}s + \epsilon(\omega)
	\end{equation}

	Where $f(t)$ is the realization of a random function in $\mathbb{L}^2[0,1]$ and $\beta(t)$ is an unknown coefficient function. 
	Similar to the finite dimensional setting, an interesting question is how to estimate the unknown function $\beta(t)$ given a data set containing realizations of a random function and associated scalar response variables. However, a simple extension of the OLS estimator to allow for infinite dimensional objects is not possible. Therefore, other options have to be considered.

	\subsection{Estimation via Basis-Representation}
	The most common way to make this problem tractable is via a basis representation of $\beta(t)$. Therefore, let $\{b_i(t) \: \vert \: i \in \mathbb{N}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.

	\begin{equation}
		\beta(t) = \sum_{j = 1}^{\infty} \psi_j b_j(t)
	\end{equation}

	This enables us to write equation \ref{DGP} with $\beta(t)$ represented in this way to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} \psi_j  b_j(s)\right) F(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j = 1}^{\infty} \left[\psi_j \textcolor{red}{\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s}\right] + \epsilon(\omega) \\
			& = \alpha + \sum_{j = 1}^{\infty} \psi_j \textcolor{red}{\langle F(\omega), b_j \rangle} + \epsilon(\omega) 
			  = \alpha + \sum_{j = 1}^{\infty} \psi_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
		\end{split}
	\end{equation}
